%-------------------------
% Resume in Latex
% Author : Shorno Kamal Roy
% Based off of: harshibar / jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\fancyfoot[R]{\color{dark-grey}\footnotesize \textit{Last updated: June 4, 2026}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Shorno Kamal Roy} \\ \vspace{5pt}
    \small \faPhone* \hspace{2pt} \texttt{+8801841151827} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \href{mailto:fb.shorno@gmail.com}{\texttt{fb.shorno@gmail.com}} \hspace{1pt} $|$
    \hspace{1pt} \faGlobe \hspace{2pt} \href{https://www.shorno.me}{\texttt{shorno.me}}
    \\ \vspace{3pt}
    \small \faGithub \hspace{2pt} \href{https://github.com/Shorno}{\texttt{github.com/Shorno}} \hspace{1pt} $|$
    \hspace{1pt} \faLinkedin \hspace{2pt} \href{https://www.linkedin.com/in/shorno/}{\texttt{linkedin.com/in/shorno}} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt} \texttt{Dhaka, Bangladesh}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AlgoVerse}{Dec. 2025 -- Present}
      {Software Engineer (Part-time)}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Designed and shipped a \textbf{Turborepo-based commerce platform} spanning web, React Native, and a Hono backend.}
        \resumeItem{Owned a \textbf{multi-role education platform} with subdomain-scoped roles, a shared Drizzle schema, and oRPC-backed web + native surfaces.}
        \resumeItem{Built a \textbf{distributor operations SPA} covering procurement through retailer fulfillment, with print-grade invoices.}
        \resumeItem{Default stack: \textbf{TypeScript, Postgres, Drizzle, Better-Auth, oRPC} across every surface.}
      \resumeItemListEnd

    \resumeSubheading
      {AppCube}{Sept. 2024 -- Dec. 2025}
      {Frontend Developer --- Ubaky (restaurant management)}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Owned the \textbf{merchant interface in React}, the surface restaurant operators use day-to-day.}
        \resumeItem{Shipped \textbf{mobile-first responsive design} across all three role-specific apps (client, merchant, admin).}
        \resumeItem{Collaborated with the backend team on \textbf{API integration} and tightened the data flow between roles.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------

\section{PROJECTS}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{SelfShop} $|$ \emph{Reseller \& Dropshipping Commerce} $|$ \href{https://selfshop.com.bd/}{\myuline{selfshop.com.bd}}}{2026 -- Present}
          \resumeItemListStart
            \resumeItem{Built \textbf{admin, reseller, and supplier dashboards} in Next.js 16 + React 19 with Ant Design and Redux Toolkit, plus a React Native + Tamagui reseller app \href{https://play.google.com/store/apps/details?id=com.selfshop.reseller}{\myuline{live on Google Play}}.}
            \resumeItem{Real-time order fan-out via \textbf{Pusher + Firebase Cloud Messaging} with reconcile-on-foreground; typed REST clients per surface against a Laravel API the team owned.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Stock Management} $|$ \emph{Distributor Operations SPA} $|$ \href{https://mstamimenterprise.shop/}{\myuline{mstamimenterprise.shop}} $|$ \href{https://github.com/Shorno/stock-management}{\myuline{GitHub}}}{2025 -- 2026}
          \resumeItemListStart
            \resumeItem{Vite + React 19 SPA for receiving, sales, transfers, returns, and printed invoices, with \textbf{TanStack Query / Table} and Zustand for predictable data flow.}
            \resumeItem{\textbf{Immutable movement-log} data model with derived stock counts; react-pdf invoice generation; Better-Auth on a separate backend repo.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Padma Service} $|$ \emph{Services Marketplace \& CMS} $|$ \href{https://padmaservice.com}{\myuline{padmaservice.com}}}{2025 -- 2026}
          \resumeItemListStart
            \resumeItem{Bilingual Next.js 16 storefront with a Hono + oRPC API on Bun, Drizzle + Postgres, and \textbf{phone-OTP member accounts} via Better-Auth.}
            \resumeItem{Admin CMS for banners, homepage sections, blogs (TipTap), and a \textbf{user-submitted listing approval queue} with Cloudinary uploads.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Daffodil International University}{2022 -- 2026}
      {BSc in Computer Science \& Engineering}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{\textbf{CGPA}: 3.30 / 4.00 \hspace{6pt} $|$ \hspace{6pt} \textbf{Coursework}: Data Structures, Algorithms, Databases, Operating Systems, Software Engineering, Web Engineering.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}  {: TypeScript, JavaScript, SQL (PostgreSQL), HTML/CSS}\vspace{2pt} \\
     \textbf{Frameworks} {: Next.js, React 19, React Native (Expo), Hono, oRPC, Drizzle ORM, Better-Auth, Tailwind CSS, shadcn/ui, Ant Design, TanStack Query}\vspace{2pt} \\
     \textbf{Tools}      {: Turborepo, pnpm, Vite, Pusher, Cloudinary, Neon, Hostinger VPS, Coolify, Git / GitHub, Figma}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
